How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-29 tse-paper/content.tex
Huge review and redo

% TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730

@@

We implement and evaluate three chunk retrieval techniques:
\begin{itemize}
  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (referred to as CTS), and
  \item keyword search (referred to as KWS).
\end{itemize}
% TODO: Shortly describe each of these techniques

\textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
\textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.

@@

We recommend PBE for use cases where the desired information is always
represented in the same structural way and high confidence in precision and
recall of the chunk retrieval is required.
CTS is well suited when the representation of the desired information varies
slightly and the output of the chunk retrieval is further processed by a human.
In cases where the textual representation of the desired information in the log
is unpredictable or varies greatly, KWS ssems to be the best choice. However, its low precision---it extracts a context of multiple lines around a find---makes it generally unsuited for automatic on-ward processing and instead requires a human to interpret the output chunk.

%\todo{structure overview of article}

\section{Related Work}
\label{sec:rw}
We explain how researchers gather information about CI usage in software projects
through build log analysis and why the chunk retrieval techniques we investigate
simplifies their data collection.
This section moves on to past works about augmenting build logs to make it easier
for developers to inspect them.
The presented approaches are related to and can benefit from the techniques we
analyze in this article.
Further, we classify build logs as semi-structured data and differentiate our
work from system log analysis.

@@

\subsection{Augmentation of Build Logs}
\label{sec:rw-bl-analysis}
Build logs are a valuable data source for developers to find out why their build failed.
Several researchers are looking into supporting developers to process the verbose build logs.
Vassallo et al.~\cite{vassallo2018un-break} try to shorten the time it takes developers to understand build logs.
They parse Maven~\cite{maven2019website} build logs into a structured representation and create hint generators.
%The hint generators leverage this structured access to the information within the build log to propose fixes.
For example, one of the hint generators queries stack overflow for discussions related to why the build failed.
In a qualitative study they observed that highlighting the locality and context of an issue is helpful to programmers.
%Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
The chunk retrieval techniques we compare in this article can be used to fill similar structured representations with information from build logs.
As they simplify the construction of parsers they would enable developers and researchers to cover a wider array of build tools, which is the main influence factor on the structure of a build log.

@@

Programming by Example (PBE) is a form of generalized program synthesis that enables users to automate repetitive tasks, without them having to explicitly code a program. The users provide examples for the input and the desired output and a
synthesis algorithm tries to create a program that transforms the input to the output, hopefully as close as possbile to the user's intention.
This section introduces the theoretical foundations of the program synthesis
algorithm of the \emph{PROgram Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
The PROSE framework is developed by Microsoft Research.
Next, this section presents the FlashExtract DSL, which defines text extraction
tasks within PROSE and is the basis for the implementation of our chunk retrieval technique PBE\@.

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=\columnwidth, clip]{img/build-overview.pdf}
	\caption{The different entities related to a CI build.
        %\todo{mention in text or remove}
        }
	\label{fig:build-overview}
\end{figure}

\subsection{Characteristics of Chunk Retrieval Techniques}
\label{sec:blirt}
In this article, we evaluate different techniques to automatically retrieve pieces of information that appear literally in the build logs, i.e., techniques that do not aggreagte, combine, or deducted information. We call such pieces of information from build logs \emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
The techniques we investigate here do not require to parse the entire structure of build logs, but focus on extracting just one specific piece of information per configuration.

With the term \textit{configuration,} we want to abstract over the training and parametrization that techniques require in different forms.
The user provides a \textit{configuration} that specifies which information the chunk retrieval should target and supplies the necessary information for the technique to identify the targeted information chunk in a build log.
Each chunk retrieval has a specific \textit{granularity}, i.e.,\ the smallest retrievable text piece and uses a specific \textit{identification technique} to select the log parts it retrieves. The granularity might be adjustable by configuration.
A \emph{run} of a chunk retrieval technique consumes a build log as a plain text file and produces a string output, which consists of substrings of the build log text.

The following sections of this section introduce the three chunk retrieval techniques we investigate: program synthesis by example (PBE), common text similarity (CTS), and keyword search (KWS).
Lastly we describe other techniques which can also be treated as chunk retrieval techniques.
Table~\ref{tab:ctr} shows a comparison of the presented techniques.

@@

@@

\subsubsection{Configuration}
In/output examples are the main driver of Programming by Example, we refer to them
as \emph{examples}.
The \emph{input} is a whole build log, i.e.\ the whole text of the build log file.
The \emph{output} is a substring of the log file text, representing the substring that should be retrieved by the synthesized program when given the corresponding input file.
One or multiple examples, the training set, configure a chunk retrieval with PBE:
they define the substring of a build log that should be extracted.
The PROSE program synthesis then tries to construct a regular expression program consistent with all training examples.
% A program is consistent with an example if it returns the defined output when executed on the defined input~\cite{mitchell1982generalization}.
PBE reports an error back to the user if it could not synthesize a consistent program.
% The program synthesis builds on the FlashExtract DSL, which in turn uses the FlashMeta algorithm.
% Both are described in Section~\ref{sec:rw-prose}.

\subsubsection{Application}
A run of PBE takes a build log file as input and applies the synthesized regular expression program.
It then returns the substring of the build log matched by the program or an empty string if the program found no match.

\subsubsection{Configuration}
To configure chunk retrieval though text similarity we chose to use the same concept of examples as for PBE\@ and apply the Vector Space Model~\cite{schutze2008introduction}.
The lines of the output strings of the training examples define our search query.
The algorithm splits the search query into single lines and identifies tokens, in our case words.
Then we build a document-term-frequency matrix over the lines from the search query and prune very often or very rarely appearing words.
Next, the algorithm applies TF-IDF to the matrix, a best practice for natural language queries~\cite{lee1997document}.

\subsection{Keyword Search (KWS)}
\label{sec:expl-skws}
When developers are looking for a specific piece of information within a large amount of unstructured information, a first ad-hoc approach they use is searching for related keywords.
Indeed, this was one of the most common approaches we took when searching for the reason the build failed within a log while creating the \emph{LogChunks} data set.
% As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is suitable for retrieving information chunks from CI build logs.
% In the following we will explain how we use simple keyword search to retrieve information from CI build logs, which we refer to as \emph{KWS}\@.

\subsubsection{Configuration}
A set of keywords configures the chunk retrieval with KWS\@.
To better compare KWS with PBE and CTS, we also configure it through examples.
We link each example with keywords, which appear in the targeted chunk or close to it in the input build log.
The configuring keywords for KWS are the ones that appear most often in the keywords of all training examples.

@@

\noindent
\textbf{Random Line Retrieval (RLR)}
In our evaluation, we want to compare against a baseline of randomly extracted lines.
The average number of lines in the outputs of the training examples is the configuration for random line retrieval (RLR).
It retrieves this number of lines randomly sampled from the build log.

@@

\section{Systematic Literature Survey and Mapping}
\label{sec:survey}
% TODO (Caro): Integrate Kitchenham's guidelines
From our own experience, we know that the field of analyzing build
logs is relatively young, with perhaps the work on TravisTorrent the
most cited and central one. We also know there have been scattered
research efforts on build log analysis prior to it, mostly where the
log analysis was a side-part of the article. To the best of our
knowledge, there has not been an attempt to systematically overview
and survey them, despite their forseeable future and current importance.

\subsection{Article Classification}
%todo

\section{Study Design}
\label{sec:study}
To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build
logs we evaluate them on the \emph{LogChunks}~\cite{brandt2020logchunks} data set.
This section describes our study design and which metrics we measure to answer our research questions.
In the presentation of the results, we first focus on each of the three techniques and later compare them against each other.

@@

\begin{figure*}[!t]
	\centering
	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
	\caption{Study design of our technique comparison study.}
	\label{fig:study}
\end{figure*}

@@

\noindent
\textbf{Training and Test Set}
We use \emph{LogChunks} as the data set for our study.
For each of the 80 repositories in it, it contains 10 build logs, manually labeled with the substring describing the reason the build failed.
Additionally, it contains keywords to search for that substring and which structural category the substring belongs to.
% TODO (Caro): Add details how key words were extracted

@@

We calculate the following metrics:
\begin{itemize}
	 \itemsep0.75em
	\item True positives: $\mathit{DesiredLines} \cap \mathit{RetrievedLines}$
	\item Precision: $\dfrac{\# \mathit{TruePositives}}{\# \mathit{RetrievedLines}}$
	\item Recall: $\dfrac{\# \mathit{TruePositives}}{\# \mathit{DesiredLines}}$
	\item F$_{1}$-score: $2 \cdot \dfrac{\mathit{Precision} \cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
	\item Successful retrieval: $\mathit{true}\ \mathit{if}\ \mathit{Recall} = 1$
\end{itemize}

Precision of a chunk retrieval describes which proportion of the retrieved lines were desired.
Recall of a chunk retrieval describes which proportion of the targeted lines were retrieved.
% Throughout the presentation and discussion of our results we show these two metrics separately, as they might have a different weight when choosing a suitable technique for a task.
In addition, we calculate the F$_{1}$-score, the harmonic mean of precision and recall.
We define a successful retrieval as one where all desired lines were extracted, therefore when recall is one.

@@

\newpage
\pagebreak
\subsection{Common Text Similarity (CTS)}

\begin{figure*}
\begin{subfigure}[t]{\columnwidth}
		\centering
                \includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for an increasing training set size.}
		\label{fig:recall-precision-examplecount-CTS}

\end{subfigure}\hspace{\fill}
\begin{subfigure}[t]{\columnwidth}
		\centering
                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for an increasing number of structural categories in the training and test sets.}
		\label{fig:recall-precision-categorycount-CTS}
\end{subfigure}
\caption{Results of chunk retrieval with Common Text Similarity (CTS)}
\end{figure*}

@@

% Figure~\ref{fig:contextsizefactor-precision-recall-CTS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with CTS\@.
% The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
% The recall ranges from 30\% to 55\%.
% A retrieval size factor of 1 gives the best average F$_{1}$-score with 51\%.

% \begin{figure}[!t]
% 		\centering
% 		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-CTS.pdf}
% 		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS compared to retrieval size factors.}
% 		\label{fig:contextsizefactor-precision-recall-CTS}
% \end{figure}

\newpage
\newpage
\subsection{Keyword Search (KWS)}

\begin{figure*}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
		\label{fig:recall-precision-examplecount-KWS}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
		\label{fig:recall-precision-categorycount-KWS}
\end{subfigure}
\caption{Results of chunk retrieval with Keyword Search (KWS)}
\end{figure*}

@@

\newpage
\newpage
\subsection{Program Synthesis by Example (PBE)}

\begin{figure*}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
                		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
                \label{fig:recall-precision-examplecount-sythesisworked-PBE}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
                		\caption{Increasing number of structural categories in the training and test sets.}

                \label{fig:failure-reason-categorycount-PBE}
\end{subfigure}
\caption{Results of chunk retrieval with  Program Synthesis by Example (PBE)}
\end{figure*}

\begin{figure}[!t]
		\centering
		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
		\caption{Results of chunk retrieval with PBE.}
		\label{fig:failure-reason-PBE}
\end{figure}

\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
In 89 further cases a program was also successfully synthesized, though in 59 of the 89 cases the synthesized program yielded no output at all.
In 30 of the 89 cases the synthesized program did not extract all of the desired lines.
For these 30 cases, the average recall was 28\%.
We present an example of such an \emph{unsuccessful retrieval} in Listing \ref{lst:pbe-unsuccessful}, where the synthesized regular expression program only retrieved two of the four targeted lines.
In 173 of the 400 cases the PROSE program synthesis could not synthesize a regular expression program that is consistent with all of the training examples.

\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs compared to the number of structural categories present in the training and test examples.
It shows that the program synthesis is more likely to succeed when there are only a few categories present in the training examples.
When two structural categories are present, PROSE could in most cases not synthesize a program consistent with all training examples.
For three or more present categories PROSE could never synthesize a consistent program.

@@

\pagebreak
\subsection{Comparison of All Techniques}
\Cref{fig:success-partial-all} compares the success of chunk retrievals differentiated by techniques in our study.
CTS and KWS extract some of the desired lines in 79\% and 88.5\% of the chunk retrieval runs.
With 38.25\%, KWS also has the highest number of fully successful extractions, followed by PBE with 34.5\%.
PBE has the lowest number of partial retrievals with only 18 out of 400 chunk retrieval runs.

@@

\Cref{fig:recall-precision-singlecategory-all} and \Cref{fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
For more than one present category, the recall of PBE decreases greatly.
For CTS and KWS the values also decrease, while RLR is not affected by the number of structural categories present.

@@

% \begin{figure}[!t]
% 		\centering
% 		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-all.pdf}
% 		\caption{Precision, recall and F$_{1}$-score of all techniques compared.}
% 		\label{fig:recall-precision-all}
% \end{figure}

\begin{figure}[!t]
	\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Precision, recall and F$_{1}$-score of all techniques compared when training examples are in \emph{one} structural category.}
		\label{fig:recall-precision-singlecategory-all}
\end{figure}

\begin{figure}[!t]
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Precision, recall and F$_{1}$-score of all techniques compared when training examples are in \emph{more than one} structural categories.}
		\label{fig:recall-precision-multicategory-all}
\end{figure}

@@

@@

\noindent
\textbf{Configuration and Input}
Our study results show that chunk retrieval with PBE gives best results when the training examples are from one structural category.
This means it is suited to retrieve information chunks that always have the same surrounding structure.
To extract for example the reason a build failed, the log passage describing the failure would always have to be started and ended the same way.

>>>>

% TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
% TODO: What about the alternate solution, installing plugins to report precise data? Ie., maven plugins
% - Lots of effort
% - not a generic solution
% - how to analyze history where such plugins were not installed
% - unclear which information you want

@@

We implement and evaluate three chunk retrieval techniques:
\begin{itemize}
  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (CTS), and
  \item keyword search (KWS), an ad-hoc method for finding fitting passages by searching the whole text for the occurrence of a specific trigger word.
\end{itemize}
% TODO: Shortly describe each of these techniques

% TODO: Add running example?
\textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
\textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
% TODO: explain structural category based on running example from above?
Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.

@@

We recommend PBE for use cases where the desired information is always
represented in the same structural way and high confidence in precision and
recall of the chunk retrieval is required.
CTS is well suited when the representation of the desired information varies
slightly and the output of the chunk retrieval is further processed by a human.
In cases where the textual representation of the desired information in the log
is unpredictable or varies greatly, KWS ssems to be the best choice. However, its low precision---it extracts a context of multiple lines around a finding---makes it generally unsuited for automatic on-ward processing and instead requires a human to further inspect and interpret the output chunk.

\section{Systematic Literature Survey and Mapping}
\label{sec:survey}

% TODO (Caro): Integrate Kitchenham's guidelines
From our own experience, we know that the field of analyzing build
logs is relatively young, with perhaps the work on TravisTorrent the
most cited and central one. We also know there have been scattered
research efforts on build log analysis prior to it, mostly where the
log analysis was a side-part of the article. To the best of our
knowledge, there has not been an attempt to systematically overview
and survey them, despite their forseeable future and current importance.

\subsection{Article Classification}
%todo Caro: please write a draft for this :-)
Having trimmed down the set of articles, we investigated them in depth.

\section{Related Work}
% TODO reorder rw by build retrieval technique rather than by paper
\label{sec:rw}
We explain how researchers gather information about CI usage in software projects
through build log analysis and why the chunk retrieval techniques we investigate
simplifies their data collection.
This section moves on to past works about augmenting build logs to make it easier
for developers to inspect them.
The presented approaches are related to and can benefit from the techniques we
analyze in this article.
Further, we classify build logs as semi-structured data and differentiate our
work from system log analysis.

@@

\subsection{Augmentation of Build Logs}
\label{sec:rw-bl-analysis}
Build logs are a valuable data source for developers to find out why their build failed.
Several researchers investigate how to support developers in working with verbose build logs.
Vassallo et al.~\cite{vassallo2018un-break} try to shorten the time it takes developers to understand build logs.
They parse Maven~\cite{maven2019website} build logs into a structured representation and create hint generators.
%The hint generators leverage this structured access to the information within the build log to propose fixes.
For example, one of the hint generators queries stack overflow for discussions related to why the build failed.
In a qualitative study they observed that highlighting the locality and context of an issue is helpful to programmers.
%Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
The chunk retrieval techniques we compare in this article can be used to fill similar structured representations with information from build logs.
As they simplify the construction of parsers they would enable developers and researchers to cover a wider array of build tools, which is the main influence factor on the structure of a build log.

@@

Programming by Example (PBE) is a form of generalized program synthesis that enables users to automate repetitive tasks, without them having to explicitly codify a computer program. One has to provide prototypical examples of the input and the desired output. A
synthesis algorithm tries to create a program (based on a regular language) that transforms the input to the output. The minimum working condition is for this when replayed on the examples inputs is to provide the specified output, but, hopefully, PBE is as close as possbile to the user's intention and thus also works on a different and larger set of inputs.
This section introduces the theoretical foundations of the program synthesis
algorithm of the \emph{PROgram Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
The PROSE framework is developed by Microsoft Research.
Next, this section presents the FlashExtract DSL, which defines text extraction
tasks within PROSE and is the basis for the implementation of our chunk retrieval technique PBE\@.

@@

\subsection{Characteristics of Chunk Retrieval Techniques}
\label{sec:blirt}
In this article, we evaluate different techniques to automatically retrieve pieces of information that appear literally in the build logs, i.e., techniques that do not aggreagte, combine, or deducted information. We call such pieces of information from build logs \emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
The techniques we investigate here do not require a formal lexer and parser to analyze the entire structure of build logs, but focus on ad-hoc extracting just one specific piece of information per configuration.

With the term \textit{configuration,} we abstract over the training and parametrization that different techniques require in different forms. A configuration can be explicitly stated or implicitly dervied by learning through provided examples. It is therefore a manual specification of which information the chunk retrieval should target. It also supplies the necessary information for the technique to identify the targeted information chunk in a build log.
Each chunk retrieval technqiue has a specific \textit{granularity}, i.e.,\ the smallest piece of text it can return (e.g., a line, or a word). The granularity might be adjustable by configuration.
\emph{Running a chunk retrieval technique} means to execute a fully configured technique to consumes as input a build log in plain text format and to produce an array as output. The array consists of substrings of the build log text.

\Cref{tab:ctr} shows a comparison of the presented techniques.

@@

\subsubsection{Configuration}
To configure chunk retrieval though text similarity we chose to use the same concept of examples as for PBE\@
% TODO Caro: More details on this. How do you 'apply' VSM? On what?
and apply the Vector Space Model~\cite{schutze2008introduction}.
The lines of the output strings of the training examples define our search query.
The algorithm splits the search query into single lines and identifies tokens, in our case words.
Then we build a document-term-frequency matrix over the lines from the search query and prune very often or very rarely appearing words.
Finally, the algorithm applies TF-IDF to the matrix, a best practice for natural language queries~\cite{lee1997document}.

\subsection{Keyword Search (KWS)}
\label{sec:expl-skws}
When developers scavenge for a specific piece of information within a large amount of unstructured information, a first ad-hoc approach they use is to search for related keywords.
Indeed, this was one of the most common approaches we took when searching for the reason the build failed within a log while creating the \emph{LogChunks} data set~\cite{logchunks}.
% As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is suitable for retrieving information chunks from CI build logs.
% In the following we will explain how we use simple keyword search to retrieve information from CI build logs, which we refer to as \emph{KWS}\@.

\subsubsection{Configuration}
A set of keywords configures the chunk retrieval with KWS\@.
To better compare KWS with PBE and CTS, we also configure it through examples.
We associate each example with keywords which appear in the targeted chunk or close to it.
The configuring keywords for KWS are the ones that appear most often in the keywords of all training examples.
% TODO Caro Please explain above sentence more precisely

@@

\subsubsection{Configuration}
In- and output example pairs are the main driver of Programming by Example, we refer to them in short
as \emph{examples}.
The \emph{input} is the text of the build log file.
The \emph{output} is an array of substrings of the log file text, representing the substrings that should be retrieved by the synthesized program when given the corresponding input file.
One or multiple examples, the training set, \emph{configure} a specific chunk retrieval with PBE:
they define the substring of a build log that should be extracted.
The PROSE program synthesis then tries to construct a program consistent with all training examples.
% A program is consistent with an example if it returns the defined output when executed on the defined input~\cite{mitchell1982generalization}.
PBE reports an error back to the user if it could not synthesize a consistent program.
% The program synthesis builds on the FlashExtract DSL, which in turn uses the FlashMeta algorithm.
% Both are described in Section~\ref{sec:rw-prose}.

% TODO Caro: The following is very obvious and could apply to any technique. 
\subsubsection{Application}
A run of PBE takes a build log file as input and applies the synthesized regular expression program.
It then returns the substring of the build log matched by the program or an empty string if the program found no match.

\subsection{Random Line Retrieval}
\label{sec:r:rlr}

In our evaluation, we want to compare against a baseline of randomly picking lines from the build log. RLR essentially mimicks the situation of guessing purely blindly which lines might be interesting.
The only configuration option for RLR is the number of lines it should return. For a fair comparison to the other techniques (whose number of returned lines is dynamic), we configure RLR to return the average number of lines in the chunks of the training examples. 
% TODO Caro: some more details here?

@@

@@

\section{Study Design}
\label{sec:study}

% TODO Caro: I find this figure still very confusing :'(, due to a lack of structure. If you want me to, I can give it a go?
\begin{figure*}[tb]
	\centering
	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
	\caption{Study design of our technique comparison study.}
	\label{fig:study}
\end{figure*}

To investigate which techqnique is best suited to retrieve chunks from CI build
logs we evaluate them on the \emph{LogChunks}~\cite{brandt2020logchunks} data set.
This section describes our study design and which metrics we measure to answer our research questions.
In the presentation of the results, we first focus on each of the three techniques and later compare them against each other.

@@

@@

\noindent
\textbf{Training and Test Set}
We use \emph{LogChunks} as the data set for our study.
For each of the 80 repositories in it, \emph{LogChunks} contains 10 build logs, manually labeled with the substring or \emph{chunk} describing the reason the build failed.
Additionally, it contains (1) keywords useful to
% TODO Caro uniquely?
identify the substring in the log  and (2) which structural category the substring belongs to.
% TODO (Caro): Add details how key words were extracted. Add example?

@@

We calculate and define a number of metrics for the context of our evaluation.

\vspace{0.2cm}
\begin{itemize}[leftmargin=0.4cm]
	 \itemsep1em
	\item $|\mbox{True positives}| = \mathit{DesiredLines} \cap \mathit{RetrievedLines}$ \vspace{0.2cm}\\
        True positives are lines that appear both in the output of a tool as well as what \textit{LogChunks} contains for each example. 
        % TODO (Caro) What about when a line is replicated twice? I.e., Are line numbers part of this?
	\item $\mbox{Precision} = \dfrac{|\mathit{True\ Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
        Precision of a chunk retrieval describes which proportion of the retrieved lines were actually desired. 
	\item $\mbox{Recall} = \dfrac{|\mathit{TruePositives}|}{|\mathit{DesiredLines}|}$ \vspace{0.2cm} \\
        Recall of a chunk retrieval describes which proportion of the desired lines were retrieved.
	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision} \cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$ \vspace{0.2cm}\\
        In addition, we calculate the F$_{1}$-score, the harmonic mean of precision and recall. We prefer F$_{1}$ to other aggregate measures such as accuracy because for a ``needle-in-the-haystack'' scenario, we do not want to bloat our results by correctly not finding lots of irrelevant log lines.
	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\ \mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\ We define a successful retrieval as one where all desired lines were extracted, therefore when recall is one.
\end{itemize}

@@

\subsection{Common Text Similarity (CTS)}
\label{sec:r:cts}
\begin{figure*}
\centering
    \textbf{Common Text Similarity (CTS)}\par\medskip
\begin{subfigure}[t]{\columnwidth}
		\centering
                \includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
		\label{fig:recall-precision-examplecount-CTS}

\end{subfigure}\hspace{\fill}
\begin{subfigure}[t]{\columnwidth}
		\centering
                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
		\label{fig:recall-precision-categorycount-CTS}
\end{subfigure}
\caption{Results of chunk retrieval with Common Text Similarity (CTS)}
\end{figure*}

@@

\subsection{Keyword Search (KWS)}
\label{sec:r:kws}
\begin{figure*}
\centering
    \textbf{Keyword Search (KWS)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
		\label{fig:recall-precision-examplecount-KWS}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
		\label{fig:recall-precision-categorycount-KWS}
\end{subfigure}
\caption{Results of chunk retrieval with Keyword Search (KWS)}
\end{figure*}

@@

\subsection{Program Synthesis by Example (PBE)}
\label{sec:r:pbe}
\begin{figure*}
\centering
    \textbf{Program Synthesis by Example (PBE)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
                		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
                \label{fig:recall-precision-examplecount-sythesisworked-PBE}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
                		\caption{Increasing number of structural categories in the training and test sets.}
                \label{fig:failure-reason-categorycount-PBE}
\end{subfigure}
\caption{Results of chunk retrieval with  Program Synthesis by Example (PBE)}
\end{figure*}

\begin{figure}[tbp]
		\centering
		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
		\caption{Results of chunk retrieval with PBE.}
		\label{fig:failure-reason-PBE}
\end{figure}

\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
In 89 further cases, an extraction program was also successfully synthesized, though in 59 of the 89 cases the synthesized program yielded no output.
In 30 of the 89 cases did the synthesized program only partially extract a subset of the desired lines.
For these 30 cases, the average recall was 28\%.
Listing \ref{lst:pbe-unsuccessful} shows an example of such an \emph{unsuccessful retrieval}, where the synthesized program only retrieved two of the four targeted lines.
In 173 of the 400 cases could PROSE not synthesize program consistent with all of the training examples.

\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs depend on the number of structural categories in the training and test examples.
The figure demonstrates that program synthesis mostly returns exactly the desired output when there are is only one structural category present in the training examples.
However, when two or more structural categories are simultaneously present in the examlpe set, PROSE could in most cases not synthesize a program consistent with all training examples.
For four or more present categories PROSE could never synthesize a consistent program.

@@

\subsection{Random Line Retrieval}
\label{sec:r:rlr}

In our evaluation, we want to compare against a baseline of randomly picking lines from the build log. Due to the fact no one would seriously consider RLR in real-world scenarios, we are omitting its detailed graphs here. However, its results follow intuitive expectations:
% TODO Caro: shortly descibre RLR graphs ommitted

\subsection{Comparison of All Techniques}
In this section, we aggregate the results from \Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr} and put them next to it each other.

\Cref{fig:success-partial-all} compares the success of chunk retrievals differentiated by techniques in our study.
CTS and KWS extract some of the desired lines in 79\% and 88.5\% of the chunk retrieval runs.
With 38.25\%, KWS also has the highest number of fully successful extractions, followed by PBE with 34.5\%.
PBE has the lowest number of partial retrievals with only 18 out of 400 chunk retrieval runs.

@@

\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
For more than one category being present, the recall of PBE decreases greatly.
For CTS and KWS the values also decrease, while RLR is not affected by the number of structural categories present.

@@

\begin{figure*}
\centering
    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{one} structural category.}
		\label{fig:recall-precision-singlecategory-all}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
                		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{more than one} structural categories.}
		\label{fig:recall-precision-multicategory-all}
\end{subfigure}
\caption{Comparison of all chunk retrieval techniques, split by structural category count.}
\end{figure*}

@@

% TODO Rather than giving them once (``friss und stirb''), better to incorporate these RQs into the text where they are being answered

@@

\noindent
\textbf{Configuration and Input}
Our study results show that chunk retrieval with PBE gives best results when the training examples are structurally identical. This is because PROSE has difficulty synthesizing OR-based programs (see \Cref{sec:prose:impl}).
PBE is thus suited to retrieve information chunks that always have the same surrounding or defining internal structure.
To extract for example the reason a build failed, the log passage describing the failure would always have to be started and ended the same way.
